Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-11-16 inst/examples/20170201-manuscript.Rmd
ok

---
title: "Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828"
author: "Mikko Tolonen, Leo Lahti, Hege Roivainen, Jani Marjanen"
date: "`r Sys.Date()`"
output: 
  beamer_presentation:
    theme: "boxes"
    colortheme: "orchid"
    fonttheme: "professionalfonts"
    dev: "png"
  pdf_document:
    dev: "svg"
fontsize: 12pt
---

```{r init, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
# Default time span
min.year <- 1488
max.year <- 1828
library(ggthemes)
library(ggmap)
library(gisfin)
library(stringr)
library(dplyr)
library(tidyr)
library(reshape2)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)
library(devtools)
# install_github("ropengov/gisfin")
# devtools::install_github('cttobin/ggthemr')
#library(ggthemr)
#knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/", dev="CairoPNG")

>>>>

---
title: "Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828"
author: "Mikko Tolonen, Leo Lahti, Hege Roivainen, Jani Marjanen"
date: "`r Sys.Date()`"
output: 
  beamer_presentation:
    theme: "boxes"
    colortheme: "orchid"
    fonttheme: "professionalfonts"
    dev: "png"
fontsize: 12pt
---

```{r init, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
# Default time span
min.year <- 1488
max.year <- 1828
library(ggthemes)
library(ggmap)
library(gisfin)
library(stringr)
library(dplyr)
library(tidyr)
library(reshape2)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)
library(devtools)
